\section{Model and Approach}
\label{sec:approach}

In this section, we detail the system model and the design goals.
We then discuss the challenges to achieve our goals.
Lastly, we introduce our random sampling-based approach.

\subsection{System Model and Goals}
\label{sec:approach:model}

In this work, we assume a decentralized, permissionless network.
Nodes can join and leave the network freely.
Each node possesses some persistent storage device(s) to store data.
For simplicity, we assume equal storage capacity on each node;
handling node heterogeneity is discussed in \XXX.
The network is assumed to be partially synchronous.
\lijl{Could we handle asynchronous network? I guess if network asynchrony is longer than node lifetime, then we can't guarantee availability.}

Nodes do not trust each other.
Honest nodes are rational \footnote{A node is rational if its actions maximize its expected profit.} and follow the protocol precisely.
Byzantine nodes can deviate arbitrarily from the protocol, and may behave irrationally.
Each node possesses a unique private/public key pair.
Byzantine nodes are computationally bounded, and cannot subvert the cryptographic algorithms used in the paper.
We assume the presence of a Proof of Stake~\cite{} protocol that defend Sybil attacks;
as such, at most $\frac{1}{3}$ of the nodes are Byzantine at any time.
We also assume the presence of a BFT blockchain protocol~\cite{};
the blockchain guarantees safety and liveness, and exposes a cryptocurrency as incentives to the nodes.

The set of nodes in the network collectively implements a distributed storage service.
The service exposes a \code{get}, \code{put}, and \code{delete} interface.
A \code{put} stores a blob of data into the service and returns an identifier;
a \code{get} takes an identifier, and returns the blob if the data was successfully stored before;
\code{delete} takes an identifier, and removes the data if it is stored in the system.
All data are \emph{immutable};
updating an existing data requires a deletion followed by a new \code{put}.

The distributed storage service should satisfy the following design goals:

\begin{itemize}
    \item \textbf{Data Availability}: If a data blob is successfully stored in the system, subsequent retrieval of the data should return the exact blob eventually.
    \item \textbf{Storage Scalability}: The overall storage capacity should increase linearly with more participating nodes in the system.
    \item \textbf{Blockchain Efficiency}: Storing a data blob (including repair) should only require one blockchain transaction with a small, constant blockchain state size.
\end{itemize}

\subsection{Challenges}
\label{sec:approach:challenges}

\paragraph{\textbf{Availability and scalability trade-off}}
Data availability and storage scalability are common design goals for traditional distributed storage systems~\cite{ceph,bigtable,gfs,dynamo,google-storage,azure_storage,f4}.
A key enabler for these properties is centralized control.
The operator can divide the system nodes into \emph{placement groups} based on their failure domains.
Given that the operator is aware and fully controls the node physical location (e.g., rack, pod, cluster, data center, and region), they can strategically form these groups to minimize correlated failures within each group.
Therefore, data stored in a placement group have high availability guarantees.
When nodes within a group fail, the operator can add nodes to restore the redundancy, while maintaining the same minimum failure correlation.
With highly available placement groups, the system can horizontally scale the storage capacity by adding more groups, without compromising availability.

The combination of permissionless setting and irrational adversaries in a decentralized network makes simultaneous data availability and storage scalability a harder challenge.
To achieve scalability, the system needs to partition nodes into placement groups to store disjoint set of data.
However, without centralized control, no entity in the system can reliably detect failure correlation within each group.
More critically, Byzantine nodes can concentrate within a few groups;
once they collude and discard the data simultaneously, data availability can be easily compromised.
Even when group formation is done carefully~\cite{}, Byzantine entities can adapt (e.g., by leaving and re-joining with different IDs) and eventually compromise a group.
Traditional BFT protocols~\cite{} address this issue by requiring an honest majority.
However, given that a third of all nodes can be Byzantine, having an honest majority in every group violates our storage scalability requirement: adding nodes no longer results in more groups with additional capacity.

\paragraph{\textbf{Erasure coding and repair integrity}}
Erasure coding (EC), using codes such as Reed-Solomon code, Local Reconstruction Code (LRC)~\cite{azure_storage}, and regenerating codes~\cite{regen_code}, is a common technique for improving storage efficiency.
Regardless of the exact code construction, commonly deployed EC requires sufficient nodes storing \emph{unique} encoded fragments to survive simultaneous failures, so that the original data can be reconstructed.
This invariant needs to hold throughout the lifetime of each stored data.

Proper encoding generation and assignment is straightforward in the presence of a trusted, centralized service.
However, without centralized trust, fragment assignment becomes a coordination problem that requires BFT consensus.
Given that each repair involves encoding generation and assignment, a data blob requires recurring BFT transactions throughout its lifetime, violating our blockchain efficiency goal.

The presence of Byzantine nodes also introduces challenges to encoding integrity.
Unlike replication where any party can independently verify data integrity using the data hash, it is non-trivial for a node to validate the correctness of an EC encoding.
The naive solution of recording all encoding hashes in the blockchain violates our blockchain efficiency goal, since the transaction state size is no longer constant.

\subsection{The Case for Random Sampling}
\label{sec:approach:case}
