\section{Design}
\label{sec:design}

We propose \sys, a minimal DSN design that instantiates the data placement mechanism introduced in \cref{sec:approach}.
We assume the existence of an incentive token that is economically favorable to rational nodes.
For example, storage costs are more than compensated by storage rewards denominated in this token.
For simplicity, we omit data expiration and removal, and the incentive for data retrieval.

\subsection{Design Overview}

\begin{algorithm}
\caption{On-chain smart contracts.
\textsc{epoch()} returns current block height, and block$_i$ is the block at height $i$.
\textsc{Stake} and \textsc{Store} transactions are presented with simplification.}
\label{alg:contract}
\begin{algorithmic}[1]
\State \textbf{State:} $\text{stakingSet} \gets \emptyset$, $\text{dataSet} \gets \emptyset, p \gets p^\star$
\Procedure{Stake}{\pk, stake}
    \State $\text{stakingSet} \gets \text{stakingSet} \cup \{\pk\}$
\EndProcedure
\Procedure{Store}{dataHash, payment}
    \State $\text{dataSet} \gets \text{dataSet} \cup \{\text{dataHash}\}$
\EndProcedure
\Procedure{Prove}{\pk, i, dataHash, $y$, $\pi$, fragIndex, frag}
    \State Assert $i+W>\textsc{epoch}()$
    \State $(n^*, h^*) \gets \textsc{sample}(\text{stakingSet}, \text{dataSet}, \textsc{hash}({\text{block}_i}))$
    \State Assert $(\pk, \text{dataHash}) = (n^*, h^*)$
    \State Assert $\VRFVerify(\pk, \text{dataHash}, y, \text{proof})$
    \State Assert $\frac{y}{Y}<p$
    \State Assert $\textsc{hash}(\pi) = \text{fragIndex}$
    \State Assert $\ECVerify(\text{dataHash}, \text{fragIndex}, \text{frag})$
    \State Reward \pk
\EndProcedure
\Procedure{UpdateSampleRate}{}
    \State $N \gets \left|\text{stakingSet}\right|$
    \State $p \gets \frac{2N_e}{(1-f)N}$ rounded to a certain precision
\EndProcedure
\end{algorithmic}
\end{algorithm}

We show the states and algorithms of \sys's on-chain contract in \cref{alg:contract}.
The smart contract maintains two on-chain states: the current set of staking nodes and the current set of stored data hashes.
The former determines the number of nodes, which in turn determines the current sample rate $p$ via a periodical routine \textsc{UpdateSampleRate}.
We will explain the formula of $p$ in \cref{sec:design:analysis}.
The smart contract accepts three types of transactions: \textsc{Stake} transactions for node joining, \textsc{Store} transactions for clients to store data, and \textsc{Prove} transactions for nodes to prove storage and claim rewards.

As shown in \cref{alg:contract}, a \textsc{Stake} transaction adds a node to the staking set, and a \textsc{Store} transaction adds a data hash to the stored-data set.
At each block height, a random $(\text{node}, \text{data})$ pair is sampled from these states using the block hash as a seed, making the sampled pair unpredictable in advance.
If the sampled node is endorsed in the data placement group, it can submit a \textsc{Prove} transaction within a time window, including a VRF proof and the stored fragment.
The smart contract validates the node and data hash in the transaction, going through a series of assertions.
If all assertions pass, the submitting node receives token rewards.

% \subsection{Client Operations}

\begin{algorithm}
\caption{Client operations.}
\label{alg:client}
\begin{algorithmic}[1]
\Procedure{Store}{data}
    \State $h \gets \textsc{hash}(data)$
    \State Submit $\textsc{Store}(h, \text{payment})$ transaction
    \State $\text{endorsed} \gets \emptyset$
    \While{$\left|\text{endorsed}\right| < N_e$}
        \State Wait for $\textsc{Endorsed}(h, \pk, y, \pi)$
        \State Assert $\VRFVerify(\pk, h, y, \pi)$
        \State Assert $\frac{y}{Y}<p$
        \State $\text{fragIndex} \gets \textsc{hash}(\pi)$
        \State $\text{frag} \gets \ECEncode(\text{data}, \text{fragIndex})$
        \State Reply $\textsc{Endorsed}$ with $(\text{fragIndex}, \text{frag})$
        \State $\text{endorsed} \gets \text{endorsed} \cup \{\pk\}$
    \EndWhile
    \State \Return $h$
\EndProcedure
\Procedure{Retrieve}{dataHash}
    \State Broadcast $\textsc{Query}(\text{dataHash})$
    \State $\text{frags} \gets \emptyset$
    \While{$\ECDecode(\text{frags}) = \bot$}
        \State Wait for $\textsc{QueryReply}(\text{dataHash}, \text{fragIndex}, \text{frag})$
        \If{$\ECVerify(\text{dataHash}, \text{fragIndx}, \text{frag})$}
            \State $\text{frags} \gets \text{frags} \cup \{(\text{fragIndex}, \text{frag})\}$
        \EndIf
    \EndWhile
    \State \Return $\ECDecode(\text{frags})$
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Node routine}
\label{alg:node}
\begin{algorithmic}[1]
\State Synchronize blockchain states stakingSet, dataSet and $p$
\State $\text{storage} \gets \emptyset$
\For{$h \in \text{dataSet}$}
    \State $(y, \pi) = \VRFGen(\sk, h)$
    \If{$\frac{y}{Y} < p$}
        \State $\text{data} \gets \textsc{Retrieve}(h)$
        \Comment use client operation
        \State $\text{fragIndex} \gets \textsc{hash}(\pi)$
        \State $\text{frag} \gets \ECEncode(\text{data}, \text{fragIndex})$
        \State $\text{storage} \gets \text{storage} \cup (h, \text{fragIndex}, \text{frag})$
    \EndIf
\EndFor
\For{every epoch $i$}
    \For{$\textsc{Query}(h)$}
        \If{$(h, \text{fragIndex}, \text{frag}) \in \text{storage}$}
            \State Reply $\textsc{Query}$ with fragIndex and frag
        \EndIf
    \EndFor
    \State Update stakingSet and dataSet according to transactions in block$_i$
    \State \textsc{UpdateSampleRate}()
    \Comment periodically, use on-chain procedure
    \If{$p$ changed}
        \State Adjust storage accordingly
    \EndIf
    \For{\textsc{Store}(h, \_) transactions $\in$ block$_i$}
        \State $(y, \pi) = \VRFGen(\sk, h)$
        \If{$\frac{y}{Y} < p$}
            \State Send $\textsc{Endorsed}(h, \pk, y, \pi)$ to client
            \State Wait for $\textsc{EndorsedReply}(\text{fragIndex}, \text{frag})$
            \State Assert $\ECVerify(h, \text{fragIndex}, \text{frag})$
            \State $\text{storage} \gets \text{storage} \cup (h, \text{fragIndex}, \text{frag})$
        \EndIf
    \EndFor
    \State $(n, h) \gets \textsc{sample}(\text{stakingSet}, \text{dataSet}, \textsc{hash}(\text{block}_i))$
    \If{$n = \pk \land (h, \text{fragIdx}, \text{frag}) \in \text{storage}$}
        \State Submit $\textsc{Prove}(\pk, i, h, y, \pi, \text{fragIdx}, \text{frag})$ transaction
    \EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

The \textsc{Store} and \textsc{Retrieve} client operations are shown in \cref{alg:client}, and the node daemon routine is presented in \cref{alg:node}.
To \textsc{Store} a data block, a client submits a \textsc{Store} transaction with the data hash and the token payment for storage.
When nodes process the \textsc{Store} transaction, they run $\VRFGen$ locally with their $\sk$ and use the current sample rate $p$ to determine whether they are endorsed.
If endorsed, they query the client and provide VRF proofs.
The client first runs $\VRFVerify$ to validate these nodes, then encodes fragments using proof hashes as indices and sends the corresponding fragments to them.
The client concludes the store operation after sending a sufficient number of encoded fragments.

To retrieve a data block, a client sends a gossip message \textsc{Query} to \sys to discover encoded fragments.
Nodes that store relevant fragments return them to the client.
The client validates these fragments in a manner similar to proving transactions and decodes the data block from the validated fragments.

% \subsection{Node Bootstrapping}

Redundancy repair occurs when new nodes join \sys, as shown in the first half of \cref{alg:node}.
After synchronizing the on-chain state, a node runs $\VRFGen$ against the current set of stored data hashes.
For each placement group in which the newly joined node is endorsed, it queries encoded fragments and decodes the data block, same as client retrieval.
It then encodes its assigned fragment, according to the VRF proof hash, and stores them locally.

\subsection{Configure Sample Rate}

The sample rate $p$ is periodically reconfigured based on Byzantine fault rate $f$, benign failure rate of rational nodes $f'$, EC recovery threshold $k$, and the number of nodes $N$.
The parameters $f$, $f'$, and $k$ are configured statically, and $N$ is derived from the current staking-node state.
% The formula for $p$ is shown in \cref{sec:design:analysis}.
If $p$ decreases when $N$ grows, each node reruns $\VRFGen$ on the data corresponding to stored fragments and discards fragments for which it is no longer endorsed.
Conversely, if $p$ increases when the system shrinks, each node reruns the bootstrap routine and stores additional fragments.
%According to the random sampling definition (\cref{sec:approach:sample}), nodes only need to discard fragments when $p$ decreases and only need to store more fragments when $p$ increases.
Note that such reconfiguration only happens when $p$ changes, and our design minimizes data transfer during reconfiguration.

\subsection{Data Availability Proof}
\label{sec:design:analysis}

Next, we derive the target sample rate $p$ from the system parameters ($f$, $f'$, and $k$) and a target (negligible) data loss probability $\varepsilon$.
We define $f'$ as the probability that a rational node fails within one time unit.
For simplicity, we let $N$ denote the minimum number of bootstrapped nodes of all time units during a reconfiguration period.
This assumption means that, when node failures occur, there will be sufficient new nodes finish bootstrapping before the next time unit so that the number of bootstrapped nodes does not drop below $N$.
This assumption exempts us from cross-time-unit analysis, and we only need to consider simultaneous failures within each time unit.

To simplify the analysis, we will prove data availability with the help of $N_e$, which bounds the minimum number of endorsed rational nodes with high probability.
We present our data availability guarantee as the following theorem.
\begin{theorem}\label{thm:main}
With a configured $N_e$, if \sys sets sample rate to
$$p=\frac{2N_e}{(1-f)N}$$
then the probability of data loss $\varepsilon$ is bounded with
$$\varepsilon\leq \varepsilon_1+(1-\varepsilon_1)\varepsilon_2$$
where
$$\varepsilon_1\le e^{-N_e/8}$$
and
$$
\varepsilon_2=
\sum_{i=N_e-k+1}^{N_e}
\binom{N_e}{i}(f')^i(1-f')^{N_e-i}
$$
\end{theorem}
For example, we choose $N_e=80$ as the default endorsement size in evaluation (\cref{sec:eval}).
With a coding parameter $k=32$ and $f'=0.1$, which means each rational node has a 10\% probability to fail during one day, 
the bound above yields $\varepsilon\le 4.54\times 10^{-5}$, corresponding to a mean time to data loss of more than $2.20\times 10^{4}$ days (about 60.3 years).
With $f=\frac{1}{3}$ and $N=10^5$, sample rate should be set to $p=2.4\times10^{-3}$ (i.e., 0.24\%).

\begin{proof}
To prove \cref{thm:main}, we analyze the two events that can lead to data loss.
The first event ($\varepsilon_1$) occurs when the number of endorsed rational nodes is smaller than $N_e$.
For simplicity, we do not further characterize availability in this case and conservatively treat this event as data loss.
The second event ($\varepsilon_2$) occurs when enough endorsed rational nodes fail simultaneously so that fewer than $k$ rational nodes remain.
Therefore, the data-loss probability is bounded by
$$\varepsilon\leq \varepsilon_1+(1-\varepsilon_1)\varepsilon_2$$

We first bound $\varepsilon_1$ under sample rate $p$.
For a random data hash, each of the $(1-f)N$ rational nodes is endorsed independently with probability $p$.
Under a binomial model and its Chernoff lower-tail bound, the probability that the number of endorsed rational nodes is below $N_e$ is
$$
\begin{aligned}
\varepsilon_1
&=\Pr[X<N_e]\le\exp\!\left(-\frac{(\mu-N_e)^2}{2\mu}\right),\\
&X\sim\mathrm{Bin}((1-f)N,p),\ \mu=(1-f)Np
\end{aligned}
$$
Applying the conservative target $(1-f)Np=2N_e$ in \cref{thm:main}, namely setting $p$ such that the expected number of endorsed rational nodes is $2N_e$, we obtain
$$\varepsilon_1\le e^{-N_e/8}$$

Finally, for $\varepsilon_2$, we assume exactly $N_e$ nodes are endorsed and ignore any additional endorsed nodes.
Then $\varepsilon_2$ is the probability that more than $N_e-k$ rational nodes fail simultaneously, given per-node failure probability $f'$, which is
$$
\varepsilon_2=
\sum_{i=N_e-k+1}^{N_e}
\binom{N_e}{i}(f')^i(1-f')^{N_e-i}
$$
Combining the bounds for $\varepsilon_1$ and $\varepsilon_2$ yields the bound on $\varepsilon$ in \cref{thm:main}.
\end{proof}
