\section{\sys Design}
\label{sec:design}

In this section, we present \sys, the first decentralized storage system that simultaneously achieves the three properties in \cref{sec:approach:model}.
The main novelty of \sys is a distributed storage design that carefully applies random sampling (\cref{sec:approach:case}) to both data placement and erasure coding.
The design assumes a BFT blockchain that orders and executes smart contracts (\ie, transactions) with linearizability~\cite{linearizability} guarantee;
\sys is agnostic to the protocol details of the blockchain.
We also assume the blockchain provides an incentive token that is economically favorable to rational nodes.

\subsection{VRF and Rateless EC Primer}
\label{sec:design:primer}

\sys applies two algorithms in its design: verifiable random function~\cite{vrf} and verifiable rateless erasure code~\cite{verify-rateless-ec}.
We first give a primer of the two algorithms.

\paragraph{\textbf{Verifiable random function (VRF)}}
A VRF~\cite{vrf} exposes a $\VRFGen$ and a $\VRFVerify$ function.
$\VRFGen$ takes a secret key $\sk$ and an input $x$, and outputs a pseudorandom value $y$ and a proof $\pi$.
$\VRFVerify$ takes a public key $\pk$, an input $x$, a value $y$, and a proof $\pi$, and outputs a boolean indicating whether $y$ is the correct $\VRFGen$ output for $x$ under $\pk$.
A VRF satisfies the following properties:

\noindent\textbf{Pseudorandomness:} For any input $x$, the output $y$ is indistinguishable from random to any efficient adversary that does not know the secret key $\sk$.

\noindent\textbf{Uniqueness:} For any input $x$, there is a unique output $y$ that can be generated with the corresponding proof $\pi$.

\noindent\textbf{Verifiability:} Given the public key $\pk$, input $x$, output $y$, and proof $\pi$, anyone can efficiently verify that $y$ is the correct VRF output for $x$ under $\pk$ using $\VRFVerify$.

\paragraph{\textbf{Verifiable rateless erasure code}}
Rateless codes are a family of erasure codes that has a special property.
A rateless code generates an \emph{infinite} sequence of encoding symbols from $k$ source blocks.
Any $k + \epsilon$ encoding symbols can be used to reconstruct the original data.
This differs from traditional maximum distance separable (MDS) codes, such as Reed-Solomon codes, which produce a fixed number of $n$ encoding symbols from the $k$ source blocks.
Rateless erasure code exposes an $\ECEncode$ function, which accepts a data block and an index and returns the encoded fragment of that index in the sequence.
It also exposes an $\ECDecode$ function, which takes $k + \epsilon$ encoded fragments and their indices, and returns the reconstructed data block.

Internally, a rateless code such as LT codes~\cite{lt_code} and raptor codes~\cite{raptor_code} split the input data into blocks.
For each encoding symbol, it performs an XOR on some subset of the blocks.
With sufficient number of blocks, the number of possible encoding symbols (exponential to the number of blocks) is practically infinite.
To decode, the decoder performs XOR on the encoding symbols to generate symbols with lesser degrees (degree is the number of original blocks XORed to produce the symbol).
The decoder repeats the process until it generates all degree one blocks, \ie, the original blocks.

Using traditional rateless codes, a decoder cannot verify the integrity of a received encoding symbol;
performing decoding using a tampered symbol would lead to integrity violation of the data.
Verifiable rateless code~\cite{verify-rateless-ec} enables any third party to validate the integrity of a received symbol with an $\ECVerify$ function.
The scheme is also space efficient.
The third party only needs to possess a small hash of the original data and the fragment with its index to $\ECVerify$ when performing the validation.

\lijl{Like VRF, can show the verifiable rateless EC interface here, so that later text can refer to it.} \sgd{Done in the text above.}

\subsection{\sys Protocol}
\label{sec:design:proto}

An \sys deployment consists of three main components: storage nodes that provide permanent storage, clients which issue \textsc{Store} and \textsc{Retrieve} requests, and \sys smart contracts deployed on the blockchain.
\cref{alg:contract}, \cref{alg:client}, and \cref{alg:node} show the state and the pseudocode for the smart contracts, the clients, and the storage nodes, respectively.
We only require the storage nodes to submit transactions and learn the finalized transaction blocks on the blockchain, that is, storage nodes and blockchain full nodes can be disjoint.

\begin{algorithm}
\caption{On-chain smart contracts.
\textsc{epoch()} returns current block height, and block$_i$ is the block at height $i$.
\textsc{Stake} and \textsc{Store} transactions are presented with simplification.}
\label{alg:contract}
\begin{algorithmic}[1]
\State \textbf{State:} $\text{stakingSet} \gets \emptyset$, $\text{dataSet} \gets \emptyset, p \gets p^\star$
\Procedure{Stake}{\pk, stake}
    \State $\text{stakingSet} \gets \text{stakingSet} \cup \{\pk\}$
\EndProcedure
\Procedure{Store}{dataHash, payment}
    \State $\text{dataSet} \gets \text{dataSet} \cup \{\text{dataHash}\}$
\EndProcedure
\Procedure{Prove}{\pk, i, dataHash, $y$, $\pi$, fragIndex, frag}
    \State Assert $i+W>\textsc{epoch}()$
    \State $(n^*, h^*) \gets \textsc{sample}(\text{stakingSet}, \text{dataSet}, \textsc{hash}({\text{block}_i}))$
    \State Assert $(\pk, \text{dataHash}) = (n^*, h^*)$
    \State Assert $\VRFVerify(\pk, \text{dataHash}, y, \text{proof})$
    \State Assert $\frac{y}{Y}<p$
    \State Assert $\textsc{hash}(\pi) = \text{fragIndex}$
    \State Assert $\ECVerify(\text{dataHash}, \text{fragIndex}, \text{frag})$
    \State Reward \pk
\EndProcedure
\Procedure{UpdateSampleRate}{}
    \State $N \gets \left|\text{stakingSet}\right|$
    \State $p \gets \frac{2N_e}{(1-f)N}$ rounded to a certain precision
\EndProcedure
\end{algorithmic}
\end{algorithm}

\subsubsection{Node Management}
\label{sec:design:proto:mgmt}
\sys runs in a permissionless setting.
Storage nodes can join or leave the system at any time.
To join the system, a storage node submits a \textsc{Stake} transaction with its public key and staking tokens, as shown in \cref{alg:contract}.
The on-chain state maintains the set of currently staking nodes, which are the active storage nodes, in the system.
The transaction adds the node to the set, and locks up the staked tokens, in defense of Sybil attacks.
% If the node later fails to pass the storage verification tests~\cref{sec:design:proto:store}, the staked tokens will be slashed.
\sgd{We don't really have slashing in current design.}
To leave the system, an existing node submits a \textsc{UnStake} transaction (omitted in listing), which removes the node from the staking set and returns the locked tokens.
\lijl{Can add the unstake transaction to the pseudocode.} \sgd{Will add if have space.}
By checking the $\st{stakingSet}$ on-chain state, all parties can have a consistent view of the current active storage nodes.
Byzantine storage nodes can also freely join and leave the system.
However, we assume Byzantine entities are bounded by $\frac{1}{3}$ of the overall tokens, so at most $\frac{1}{3}$ of the nodes in the $\st{stakingSet}$ at any time can be Byzantine.
\lijl{Currently, we don't specify how much stake is required, and how that relates to the storage capacity of the node, or the rewards. We should discuss briefly.}
\sgd{Staking is not for correct behavior but just to defend Sybil attacks. So being sufficient to make Sybil attack too expensive is good enough.}

\begin{algorithm}
\caption{Client operations.}
\label{alg:client}
\begin{algorithmic}[1]
\Procedure{Store}{data}
    \State $h \gets \textsc{hash}(data)$
    \State Submit $\textsc{Store}(h, \text{payment})$ transaction
    \State $\text{endorsed} \gets \emptyset$
    \While{$\left|\text{endorsed}\right| < N_e$}
        \State Wait for $\textsc{Endorsed}(h, \pk, y, \pi)$
        \State Assert $\VRFVerify(\pk, h, y, \pi)$
        \State Assert $\frac{y}{Y}<p$
        \State $\text{fragIndex} \gets \textsc{hash}(\pi)$
        \State $\text{frag} \gets \ECEncode(\text{data}, \text{fragIndex})$
        \State Reply $\textsc{Endorsed}$ with $(\text{fragIndex}, \text{frag})$
        \State $\text{endorsed} \gets \text{endorsed} \cup \{\pk\}$
    \EndWhile
    \State \Return $h$
\EndProcedure
\Procedure{Retrieve}{dataHash}
    \State Broadcast $\textsc{Query}(\text{dataHash})$
    \State $\text{frags} \gets \emptyset$
    \While{$\ECDecode(\text{frags}) = \bot$}
        \State Wait for $\textsc{QueryReply}(\text{dataHash}, \text{fragIndex}, \text{frag})$
        \If{$\ECVerify(\text{dataHash}, \text{fragIndx}, \text{frag})$}
            \State $\text{frags} \gets \text{frags} \cup \{(\text{fragIndex}, \text{frag})\}$
        \EndIf
    \EndWhile
    \State \Return $\ECDecode(\text{frags})$
\EndProcedure
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Node routine}
\label{alg:node}
\begin{algorithmic}[1]
\State Synchronize blockchain states stakingSet, dataSet and $p$
\State $\text{storage} \gets \emptyset$
\For{$h \in \text{dataSet}$}
    \State $(y, \pi) = \VRFGen(\sk, h)$
    \If{$\frac{y}{Y} < p$}
        \State $\text{data} \gets \textsc{Retrieve}(h)$
        \Comment use client operation
        \State $\text{fragIndex} \gets \textsc{hash}(\pi)$
        \State $\text{frag} \gets \ECEncode(\text{data}, \text{fragIndex})$
        \State $\text{storage} \gets \text{storage} \cup (h, \text{fragIndex}, \text{frag})$
    \EndIf
\EndFor
\For{every epoch $i$}
    \For{$\textsc{Query}(h)$}
        \If{$(h, \text{fragIndex}, \text{frag}) \in \text{storage}$}
            \State Reply $\textsc{Query}$ with fragIndex and frag
        \EndIf
    \EndFor
    \State Update stakingSet and dataSet according to transactions in block$_i$
    \State \textsc{UpdateSampleRate}()
    \Comment periodically, use on-chain procedure
    \If{$p$ changed}
        \State Adjust storage accordingly
    \EndIf
    \For{\textsc{Store}(h, \_) transactions $\in$ block$_i$}
        \State $(y, \pi) = \VRFGen(\sk, h)$
        \If{$\frac{y}{Y} < p$}
            \State Send $\textsc{Endorsed}(h, \pk, y, \pi)$ to client
            \State Wait for $\textsc{EndorsedReply}(\text{fragIndex}, \text{frag})$
            \State Assert $\ECVerify(h, \text{fragIndex}, \text{frag})$
            \State $\text{storage} \gets \text{storage} \cup (h, \text{fragIndex}, \text{frag})$
        \EndIf
    \EndFor
    \State $(n, h) \gets \textsc{sample}(\text{stakingSet}, \text{dataSet}, \textsc{hash}(\text{block}_i))$
    \If{$n = \pk \land (h, \text{fragIdx}, \text{frag}) \in \text{storage}$}
        \State Submit $\textsc{Prove}(\pk, i, h, y, \pi, \text{fragIdx}, \text{frag})$ transaction
    \EndIf
\EndFor
\end{algorithmic}
\end{algorithm}

\subsubsection{Data Storage}
\label{sec:design:proto:store}
Storage nodes in \sys are egalitarian.
There is no hierarchy, no special roles or authorities, and all the nodes follow the exact same protocol.
The design philosophy minimizes centralization and permits diverse participants in the system to improve fault resilience.

As shown in \cref{alg:client} (line 1-3), to store a data blob, a client submits a \st{Store} transaction with the hash of the data and the token payment for storage.
The transaction does not include the actual data to reduce on-chain storage cost.
The transaction adds the data hash to the \st{dataSet} on-chain state (\cref{alg:contract} line 5-7), which maintains the current set of data stored in the system.

Storage nodes subscribe to the blockchain (\cref{alg:node}).
For any \st{Store} transaction in a new finalized block (line 23-26), a node performs the following sampling procedure to determine if it is \emph{endorsed} to store the data.
It runs $\VRFGen$ with its secret key and the data hash $h$ in the transaction as input, obtaining a pseudorandom output $y$ and a proof $\pi$.
Suppose the maximum $\VRFGen$ output is $Y$, the node calculates a ratio $\frac{y}{Y}$.
If the ratio is below a public target sampling rate $p$, the node is endorsed to store the data.
The sampling rate $p$ is stored on-chain (\cref{alg:contract} line 1);
we discuss how $p$ is configured in \cref{sec:design:param}.
For data with hash $h$, this endorsement procedure forms a placement group $\mathcal{P}$:
$$\mathcal{P}(h)=\left\{n\in\mathcal{N}\mid\frac{\VRFGen(\sk_n,h)}{Y}<p\right\}$$
where $\mathcal{N}$ is the set of all nodes.
By properly setting the sampling rate, sufficient honest nodes will independently join the placement group with overwhelming probability to provide data availability.
Guarantees of VRF ensure that Byzantine nodes cannot tamper with the endorsement of honest nodes.

Endorsed nodes then send an \textsc{Endorsed} message to the client with their public keys, the VRF output and the VRF proof.
The client (\cref{alg:client} line 4-13) verifies the endorsement by invoking $\VRFVerify$ and similarly calculates the ratio $\nicefrac{y}{Y}$.
It sends erasure coded data fragments to the verified endorsed nodes.
As introduced in \cref{sec:approach:case}, we use a sampling-based approach to independently select random fragments for the endorsed nodes.
To ensure each endorser selects a unique fragment with high probability, we perform sampling on the infinite encoding space of a verifiable rateless EC (\cref{sec:design:primer}).
Compared to the straw man solution that samples multiple fragments proposed in \cref{sec:approach:case}, the rateless EC-based solution achieves theoretically optimal storage efficiency (one fragment per node), while maintaining the same disjoint fragment selection property.
Specifically, we use the VRF proof of the endorsed node as the sampling seed, hashing it to obtain a fragment index in the encoding space.
The client then performs $\ECEncode$ to encode the corresponding fragment and sends to the endorsed node.
The client repeats the process until it contacts sufficient endorsed nodes which guarantee data availability.
When a storage node receives an EC fragment (\cref{alg:node} line 27-30), it applies $\ECVerify$ of the verifiable rateless EC to validate fragment integrity.
It then adds verified fragments to its local permanent storage.

\subsubsection{Storage Verification}
\label{sec:design:proto:pos}
To incentivize storage nodes to store their endorsed data, \sys applies a storage verification protocol.
Note that we assume that the mechanism is only effective for rational honest nodes;
irrational Byzantine nodes may ignore these incentives and discard stored data.
However, our sampling-based solution (\cref{sec:design:proto:store}) always maintain data availability.

Specifically, at each blockchain block height, every storage node invokes a \textsc{sample} procedure that takes the current contract state and the latest block hash as inputs, and outputs a sampled (node, data) pair (\cref{alg:node} line 32-35).
Randomness of the inputs ensure that the output (node, data) pair is statically unpredictable.
If the storage node is sampled, and it is endorsed to store the data, it can submit a \textsc{Prove} transaction that includes its VRF proof and the stored EC fragment.
The smart contract (\cref{alg:contract} line 8-17) performs the same \textsc{sample} procedure and verifies that the submitting node and data are the sampled result.
It then validates the VRF proof, ensures that the node is endorsed, and checks the integrity of the EC fragment.
If all checks pass, the contract transfers some reward tokens to the submitting node.
To maximize rewards, a rational honest node will maintain storage of all endorsed data fragments.

\subsubsection{Data Retrieval}
\label{sec:design:proto:retrieval}
To retrieve a data blob (\cref{alg:client} line 16-26), a client broadcasts a gossip message \textsc{Query} with the data hash to all storage nodes.
In \cref{sec:impl:dht}, we discuss an optimized design that reduces the overhead of this global broadcast.
When a storage node processes the \textsc{Query} message (\cref{alg:node} line 13-17), it searches its local storage to check if it has stored an EC fragment of the queried data.
Each node maintains an in-memory hash map to speed up the search process.
On a hit, the node responds the EC fragment to the client.
The client validates the integrity of the received fragments.
Once it receives sufficient correct fragments, it performs $\ECDecode$ to reconstruct the original data blob.

\subsubsection{Repair}
\label{sec:design:proto:repair}
When honest nodes permanently fail or leave, \sys needs to repair impacted data redundancy to maintain data availability.
Prior solutions rely on centralized monitoring and coordination to repair redundancy.

Being a decentralized storage system, \sys applies a different approach to data repair.
When the overall system size remains relatively stable, \sys relies on newly joined nodes to repair lost redundancy due to churns.
Specifically, after a new node joins the system and synchronizes the on-chain state (\cref{alg:node} line 1-11), it iterates through all the stored data hashes in \st{dataSet}.
For each data hash, the node performs the same VRF-based sampling to check endorsement.
If the node is endorsed, it requests the EC fragments from other storage nodes and reconstruct the original data, identical to the client retrieval procedure.
Subsequently, the node encodes its sampled EC fragment (same as the \textsc{Store} procedure), and stores the fragment locally.
Our sampling mechanism ensures that the newly joined honest nodes will restore the required redundancy in each placement group with high probability.

When the system size changes due to node churns, \sys updates the public sampling rate $p$ to match this change.
In \cref{sec:design:param}, we detail how storage nodes reconfigure their storage when $p$ changes.

\subsection{System Parameter Configuration}
\label{sec:design:param}
A critical parameter in \sys is the public sampling rate $p$.
$p$ is periodically reconfigured based on the Byzantine fault rate $f$, benign failure rate of rational nodes $f'$, EC recovery threshold $k$, and the number of current active nodes $N$.
The parameters $f$, $f'$, and $k$ are configured statically, and $N$ is derived from the current on-chain $\st{stakingSet}$ state.
\cref{sec:design:proof} explains how we derive the exact $p$ value.
% The formula for $p$ is shown in \cref{sec:design:analysis}.
Storage nodes react to changes in $p$ (\cref{alg:node} line 20-22).
If $p$ decreases when $N$ grows, each node reruns $\VRFGen$ on its locally stored EC fragments and discards fragments for which it is no longer endorsed.
Conversely, if $p$ increases when the system shrinks, each node reruns the bootstrap routine (line 3-11) and stores additional endorsed fragments.
%According to the random sampling definition (\cref{sec:approach:sample}), nodes only need to discard fragments when $p$ decreases and only need to store more fragments when $p$ increases.
Note that such reconfiguration only happens when $p$ changes, and our design minimizes data transfer during reconfiguration.

\subsection{Correctness Proof}
\label{sec:design:proof}
We now formally prove that the \sys protocol guarantees data availability.
To do so, we derive the target sample rate $p$ from the system parameters ($f$, $f'$, and $k$) and a target (negligible) data loss probability $\varepsilon$.
We define $f'$ as the probability that a rational node fails within one time unit.
For simplicity, we let $N$ denote the minimum number of bootstrapped nodes of all time units during a reconfiguration period.
This assumption means that, when node failures occur, there will be sufficient new nodes finish bootstrapping before the next time unit so that the number of bootstrapped nodes does not drop below $N$.
This assumption exempts us from cross-time-unit analysis, and we only need to consider simultaneous failures within each time unit.

To simplify the analysis, we will prove data availability with the help of $N_e$, which bounds the minimum number of endorsed rational nodes with high probability.
We present our data availability guarantee as the following theorem.
\begin{theorem}\label{thm:main}
With a configured $N_e$, if \sys sets sample rate to
$$p=\frac{2N_e}{(1-f)N}$$
then the probability of data loss $\varepsilon$ is bounded with
$$\varepsilon\leq \varepsilon_1+(1-\varepsilon_1)\varepsilon_2$$
where
$$\varepsilon_1\le e^{-N_e/8}$$
and
$$
\varepsilon_2=
\sum_{i=N_e-k+1}^{N_e}
\binom{N_e}{i}(f')^i(1-f')^{N_e-i}
$$
\end{theorem}
For example, we choose $N_e=80$ as the default endorsement size in evaluation (\cref{sec:eval}).
With a coding parameter $k=32$ and $f'=0.1$, which means each rational node has a 10\% probability to fail during one day,
the bound above yields $\varepsilon\le 4.54\times 10^{-5}$, corresponding to a mean time to data loss of more than $2.20\times 10^{4}$ days (about 60.3 years).
With $f=\frac{1}{3}$ and $N=10^5$, sample rate should be set to $p=2.4\times10^{-3}$.
%(i.e., 0.24\%).

\begin{proof}
To prove \cref{thm:main}, we analyze the two events that can lead to data loss.
The first event ($\varepsilon_1$) occurs when the number of endorsed rational nodes is smaller than $N_e$.
For simplicity, we do not further characterize availability in this case and conservatively treat this event as data loss.
The second event ($\varepsilon_2$) occurs when enough endorsed rational nodes fail simultaneously so that fewer than $k$ rational nodes remain.
Therefore, the data-loss probability is bounded by
$$\varepsilon\leq \varepsilon_1+(1-\varepsilon_1)\varepsilon_2$$

We first bound $\varepsilon_1$ under sample rate $p$.
For a random data hash, each of the $(1-f)N$ rational nodes is endorsed independently with probability $p$.
Under a binomial model and its Chernoff lower-tail bound, the probability that the number of endorsed rational nodes is below $N_e$ is
$$
\begin{aligned}
\varepsilon_1
&=\Pr[X<N_e]\le\exp\!\left(-\frac{(\mu-N_e)^2}{2\mu}\right),\\
&X\sim\mathrm{Bin}((1-f)N,p),\ \mu=(1-f)Np
\end{aligned}
$$
Applying the conservative target $(1-f)Np=2N_e$ in \cref{thm:main}, namely setting $p$ such that the expected number of endorsed rational nodes is $2N_e$, we obtain
$$\varepsilon_1\le e^{-N_e/8}$$

Finally, for $\varepsilon_2$, we assume exactly $N_e$ nodes are endorsed and ignore any additional endorsed nodes.
Then $\varepsilon_2$ is the probability that more than $N_e-k$ rational nodes fail simultaneously, given per-node failure probability $f'$, which is
$$
\varepsilon_2=
\sum_{i=N_e-k+1}^{N_e}
\binom{N_e}{i}(f')^i(1-f')^{N_e-i}
$$
Combining the bounds for $\varepsilon_1$ and $\varepsilon_2$ yields the bound on $\varepsilon$ in \cref{thm:main}.
\end{proof}
