\section{Introduction}
\label{sec:intro}

Decentralized storage networks (DSNs) are emerging as a reliable and cost effective approach for long term blockchain data storage.
\xxx{Replace the following with real world examples.}
Blockchain ecosystems generate large volumes of data.
The consensus protocols produce blocks of historical transactions at high rates.
These blocks must be archived for future analysis and auditing.
In addition, blockchain applications store multimedia data for digital assets that have real economic value, so data loss can lead directly to financial loss.

DSNs address the requirement that data must be stored reliably under strict trust assumptions in which no single participant is trusted.
\lijl{Given that the reviewers might not be familiar with the concept, we should elaborate on the motivation of DSN.}\sgd{Done.}
While the centralized storage systems focus on tolerate failures of storage resources owned by the same organization, in DSNs the organization is untrusted, and DSNs strive to further tolerate the case where the whole organization fails, for example, by shutting down its storage service or censorship the stored data.
Consequently, DSNs rely on resources contributed by many permissionless providers and coordinated by distributed protocols such as smart contracts executed on blockchains.
Providers can join and leave the network at any time.
DSNs can tolerate data loss on individual nodes caused by node churn, disk failures, and adversarial behavior.
As a result, users need not trust any single provider for availability while retaining confidence that their data remain reliably stored.
DSNs are also cost effective because no single provider can monopolize storage resources.

As in centrally managed distributed storage, the central task in DSNs is to determine how data are placed across nodes.
Each data block is stored redundantly on multiple nodes so that individual node failures do not cause data loss.
For each block, the selected set of storing nodes is the placement group.
\sgd{Reworked the rest of this paragraph.}
This storage metadata must be reliably preserved over the entire lifetime of the data blocks to assist data retrieval and repairing for failures.
In some DSNs, the smart contract acts similar to the metadata servers in centrally managed storage and store data placement with on-chain state, while the other DSNs employ algorithmic data placement solutions and determine placement groups with algorithms or network protocols.
\iffalse
DSNs must determine placement groups consistently \lijl{``consistently'' here is a bit vague} over the entire lifetime of each block so that data remain retrievable at any time and storage audits \lijl{the concept of auditing has not been introduced} can be executed continuously.
Placement groups must also be large enough to tolerate correlated failures and Byzantine nodes, which requires replacing failed group members promptly when failures occur.
Most importantly, DSNs must provide incentives for rational nodes to follow the protocol and store data correctly.
For example, nodes can be required to provide proofs of retrievability~\cite{por}, which prevents them from claiming storage without actually retaining the data.
\fi

\sgd{Reworked.}
The data placement in DSNs is surprisingly challenging because of the presence of Byzantine nodes.
Byzantine nodes may behave arbitrarily and are potentially malicious.
The adversaries may attempt to cause data loss in DSNs and ignore the economic incentive that could drive the remaining rational nodes to follow the protocols.
Regarding data placement, the Byzantine nodes are especially dangerous for creating unexpected correlated failures.
The Byzantine nodes in the same placement groups can conclude with each other and discard their stored redundancy together.
In the view of DSNs, this means the placement groups will experience larger scale of simultaneous failures than the DSNs expected from independent rational nodes, because the Byzantine nodes deliberately enlarge the failure scale.
A placement group that is supposed to tolerate $m$ simultaneous failures will suddenly break at more than $m-f$ simultaneously failures, if containing $f$ Byzantine nodes.
While prior DSN designs have focused mainly on enforcing correct storage of rational nodes and efficiently detect storage failures~\cite{por}, they largely overlook the attacks targeting data placement, as in this kind of attacks no failure would occur before data loss.

\sgd{Reworked.}
For the placement groups with same number of nodes, the ones with less rational nodes (and more Byzantine nodes) are less effective in tolerating failures.
We define the \emph{effective placement group} of a data block to be the rational nodes within its placement group determined by the DSN.
The data is only available if and only if its effective placement group is sufficiently large to tolerate simultaneous failures, so the effective placement group in DSNs is conceptually closer to the placement group in centrally managed storage than its actual placement group.
Unfortunately, the DSNs cannot identify the Byzantine nodes in the placement groups and cannot determine the effective size of the placement groups.
What's worse, the Byzantine nodes can strategically choose the participated placement groups and cluster in the victim ones.
Many DSNs incentivize their placement groups to have uniform sizes to balance the redundancy of stored data.
The more Byzantine nodes in a placement group, the less rational nodes reside in it, and the placement group will eventually be compromised.

\sgd{Reworked.}
For many DSNs, the only way to defend against the Byzantine nodes clustering in single placement group is to enlarge its placement groups to outnumber the Byzantine nodes.
To tolerate a fraction (e.g., \nicefrac{1}{3}) of Byzantine nodes commonly found in permissionless systems, such large placement groups lead to impractical on-chain footprint or limited total storage volume. We review the limitations of prior DSNs in \cref{sec:motivation:review}.
In the end, no prior DSNs can achieve scalable storage volume and on-chain footprint while tolerating a fraction of Byzantine nodes.

\iffalse
Compared with traditional distributed storage, DSNs face unique challenges in data placement because of their decentralized infrastructure.
First, a fraction of network nodes is assumed to be Byzantine.
The placement strategy must therefore tolerate Byzantine nodes within placement groups without introducing excessive redundancy.
Second, most DSNs rely on blockchains to govern data placement in order to avoid dependence on any single party.
\sgd{May mention Storj as an exception if we want to.}
DSNs must operate under limited on-chain storage capacity and high on-chain operation costs.
Accordingly, they must keep the on-chain metadata overhead of data placement low, even when placement groups are large enough to tolerate high failure rates.

Prior DSN designs have focused mainly on enforcing correct behavior by rational nodes, while largely overlooking the efficiency and scalability of placement strategies under Byzantine faults.
Filecoin and Sia rely on storage contracts to govern placement, which introduces substantial on-chain storage overhead.
This overhead limits placement group size and therefore reduces tolerance to Byzantine nodes.
Arweave and Permacoin do not support erasure coding and do not enforce explicit data placement.
As a result, they must store copies on a large fraction of all nodes to tolerate Byzantine behavior, which yields unscalable redundancy.
In addition, Walrus remains vulnerable to Byzantine behavior under its committee based design and underutilizes the storage capacity of non selected nodes, while Swarm must replicate data to many nodes to tolerate Byzantine joining attacks.
In summary, existing DSNs do not simultaneously achieve storage efficiency and scalably low on-chain overhead while tolerating a Byzantine fraction of nodes.
We discuss these DSNs in more detail in \cref{sec:motivation:review}.
\fi

\sgd{Reworked.}
We identify the crux of data placement solution efficiently tolerating Byzantine nodes in DSNs.
The Byzantine nodes, unique to the permissionless decentralized storage, strategically move around placement groups to attack data placement.
Many DSNs defend these adversarial power individually from each placement group, the same as how they (and the centrally managed storage) defend benign failures, which results in excessive repeated efforts which subsequently lead to various undesirable trade-offs.
Instead, the data placement solution must be aware of the fact that it is always the \emph{same} set of Byzantine nodes attacking the system, with their limited attacking power that can only target limited number of placement groups at a time.
The DSN can take advantage from this insight by holistically determine all placement groups that collectively defend the Byzantine nodes in the network.

Following this idea, we design \sys, a DSN whose nodes are randomly sampled into every placement group\footnotemark.
\footnotetext{The name \sys is to reflect this randomization-based design.}
\sys employs verifiable random function (VRF)~\cite{vrf,vrf-rfc} to enable publicly verifiable sampling, which we call endorsement, and restrict the expected number of placement groups that endorse a node.
Even though it is still possible for the Byzantine nodes of \sys to arbitrarily choose their sampled placement groups and e.g., cluster in single placement group, the total number of endorsing all Byzantine nodes by all placement groups is controlled by the VRF and remain probabilistically constant.
Exploiting this fact, \sys allocates incentive per endorsement rather than per placement group.
For the victim placement groups clustered by Byzantine nodes, the groups receive more reward, and the rewards received by the rational nodes endorsed by the groups are not affected by the Byzantine nodes in their groups, so they are incentivized to stay in the groups.
Thus, the effective placement groups are stable no matter how Byzantine nodes distribute in the placement groups, allowing us to analysis data availability similar to centrally managed storage in \cref{sec:design:analysis}.
\sys employs erasure coding to ensure scalable storage volume.
We employ random sampling again to address the challenge of encoded fragment assignment in highly dynamic placement groups with nodes continuously joining and leaving.
We adopt verifiable rateless erasure coding~\cite{verify-rateless-ec} to further optimize for space efficiency and enable verifiable storage.

\iffalse
In this work, we propose \sys, a DSN design with efficient and scalable data placement strategy.
\sys uses erasure coding to distribute redundancy across large placement groups while maintaining low redundancy.
It stores only a global parameter and one data hash per block \lijl{what is a block?} on-chain to determine placement groups.
% It also assigns new nodes efficiently to the placement groups that require repair.
\lijl{VRF seems a concrete design option. Can give a higher level design idea first.}
The core technique in \sys is a verifiable random function (VRF)~\cite{vrf,vrf-rfc} for determining data placement.
A VRF is a cryptographic primitive that maps an input to a pseudorandom output together with a proof of correctness.
The output is unpredictable to anyone without the secret key, yet efficiently verifiable by anyone with the corresponding public key.
Using VRF, \sys determines placement in a manner that adversaries cannot predict or manipulate, without requiring additional consistent on-chain state.
\sys further employs verifiable rateless erasure coding~\cite{verify-rateless-ec} to achieve storage efficiency without incurring additional on-chain overhead.
\lijl{Similar to the previous point, should explain the higher level rationale first, before giving the concrete solution.}
The VRF output determines the encoded symbols assigned to each node in a placement group.
Rateless erasure coding generates an unbounded stream of encoded symbols from each original block, so symbols assigned by VRF are distinct with high probability.
These symbols are verifiable using only the data hash and the VRF proof, which enables \sys to audit storage and incentivize nodes accordingly.

We present the complete design of \sys around this novel data placement strategy, including the network protocols for storing and retrieving data, auditing storage, and repairing lost redundancy.
The repairing in \sys only happens when new nodes joining the network and in the rare case of a shrinking network, so it is efficient and does not involve heavyweight on-chain maintenance routines.
\fi

In \cref{sec:design}, we present the full design of \sys around its sampling-based data placement solution.
Then we show preliminary simulation results of \sys in \cref{sec:eval}.
\sys is able to persist sufficient encoded fragments for recovery during a 10-year simulation while incurring only around $2\times$ redundancy.
We also show that the Byzantine resiliency of \sys increases with more redundancy and is significantly higher than replication baseline.