\section{Motivation}
\label{sec:motivation}

\lijl{This section is too long. Should be at most 2.5 pages for the first two sections.}
\subsection{DSNs and Their Data Placement}

Decentralized storage networks (DSNs) provide blob storage services backed by resources collectively contributed by permissionless nodes.
Some nodes are rational and aim to generate profit with their storage supply, while others are Byzantine, behaving arbitrarily and potentially maliciously~\cite{bar}.
For simplicity, we assume nodes with uniform storage supply.
\sys can support heterogeneous nodes via virtual nodes~\cite{chord}, in which case tolerating a fraction of Byzantine nodes means tolerating a fraction of storage resources controlled by Byzantine identities.
\lijl{Somewhere, maybe here, clarify what Byzantine nodes can do in this context.} \sgd{Done.}
In this work, we focus on DSN data placement: which nodes should store redundant fragments for each data block, and what form that redundancy (i.e., replication or erasure coding~\cite{rs-code}) should take.

Byzantine nodes can attack DSNs by exploiting their data placement policies~\cite{ipfs-attack,bittorrent-attack}.
Even when a data block appears to be securely replicated, it can become irrecoverable if too few nodes in its placement group are rational and Byzantine nodes deliberately fail as soon as they observe sufficiently many simultaneous failures of rational nodes.
In practice, a placement group can tolerate failures only through its \emph{effective} portion, namely, its rational members.
Moreover, Byzantine nodes may strategically join specific groups to reduce their effective reliability.
As Byzantine participation dilutes rewards, rational nodes may leave, which further weakens those groups even when their nominal sizes still appear sufficient.
This kind of ``silent'' attack cannot be detected prior to actual data loss with widely studied techniques such as proof of retrievability~\cite{por}.

DSN data placement commonly relies on smart contracts and on-chain computation, which play a role similar to that of a metadata server in centrally managed storage systems.
Some DSNs explicitly materialize storage metadata as on-chain state, whereas others use algorithmic placement, where groups are derived off-chain or validated on-chain through deterministic rules.
Algorithmic placement is typically more efficient and scalable in on-chain state consumption, because its on-chain state overhead can be independent of placement-group size.
This property is critical for supporting less reliable nodes with larger groups without excessively increasing costly and non-scalable on-chain state.

\iffalse
DSNs provide reliable storage as long as the share of Byzantine nodes remains below a threshold (e.g., \nicefrac{1}{3}), ensuring stored data can be retrieved.
They incentivize rational nodes to store and serve data correctly while tolerating the presence of Byzantine nodes.

This work focuses on improving data placement strategies in DSNs.
In storage systems, data placement determines, for a given data block, which nodes should store redundant fragments and what form that redundancy takes.
These nodes are the placement group of the data block.
Redundant placement across multiple nodes is crucial for tolerating simultaneous failures.
For instance, storing $r$ copies of a data block on distinct nodes keeps the data available even if $r-1$ nodes fail concurrently.
As long as the storage system can repair the redundancy before all $r$ nodes fail, the storage remains durable.

In practice, storing a large number of full copies incurs excessive storage overhead.
Storage systems commonly employ erasure coding to achieve better storage efficiency.
They encode a data block into $n$ fragments, any $k$ of which can recover the data block, and store them on $n$ nodes.
Then, the storage systems can tolerate simultaneous failure of any combination of $n-k$ nodes while incurring only $\nicefrac{n}{k}$ times the storage of the data block across these nodes.
A common guideline is that higher node failure rates require tolerance of larger simultaneous-failure sets, which in turn motivates larger placement groups.

Compared to traditional storage systems, data placement in DSNs faces additional challenges from Byzantine nodes and limited governance infrastructure.
DSNs configured with placement groups of $n$ nodes that can tolerate $k$ simultaneous failures must ensure that no more than $f$ Byzantine nodes are selected so that $f+f'>k$, where at most $f'$ benign simultaneous failures are expected among the $n-f$ rational nodes.
Otherwise, colluding Byzantine nodes may create simultaneous failures leading to data loss.
Because the security model forbids reliance on a trusted coordinator, DSNs must use blockchains to reach consensus on placement governance to tolerate Byzantine behavior.
\lijl{Somewhere in the paper, should discuss storage metadata. DSNs use blockchain to generate and store metadata.}
Blockchains are notorious for high on-chain state cost and high transaction cost.
In DSNs, every blockchain node effectively acts as a full storage controller and replicates maintenance effort for all data blocks.
Keeping on-chain overhead low is crucial for DSNs to scale and manage large data volumes.
\fi

\sgd{Maybe propose these goals after literature review?}
In summary, we seek DSN data placement solutions that satisfy the following goals:
\begin{itemize}
    \item Tolerate up to a target fraction of Byzantine nodes;
    \item Keep storage volume scalable with the total storage supply;
    \item Keep the on-chain state footprint scalable and independent of placement-group size.
\end{itemize}

\subsection{Previous DSNs and Their Limitations}
\label{sec:motivation:review}

\begin{table}[t]
\centering
% \renewcommand{\arraystretch}{1.5}
\begin{minipage}{\columnwidth}
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}X c c c}
\toprule
Solution    & Volume                             & \shortstack{On-chain\\Footprint} & \shortstack{Fault\\Tolerance} \\
\midrule
On-chain~\cite{filecoin,sia,shelby}
            & \ProsCell $O(N\cdot S)$            & \ConsCell $O(D\cdot P)$   & \ConsCell $O(P)$          \\
Full~\cite{arweave,permacoin,retricoin}
            & \ConsCell $O(\frac{N}{P}\cdot S)$  & \ProsCell $O(1)$          & \ConsCell $O(P)$          \\
Permissioned~\cite{walrus,bft-dsn}
            & \ConsCell $O(S)$                   & \ProsCell $O(D)$          & \ConsCell $O(1)$          \\
Neighborhood~\cite{swarm}
            & \ConsCell $O(\frac{N}{P}\cdot S)$  & \ProsCell $O(1)$          & \ProsCell $O(N)$          \\
\sys        & \ProsCell $O(N\cdot S)$            & \ProsCell $O(D)$          & \ProsCell $O(N)$          \\
\bottomrule
\end{tabularx}
\end{minipage}
\caption{
    Comparison of data placement solutions in DSNs.
    $N$ indicates the total number of nodes, $S$ indicates the storage supply of each node (assuming uniform nodes), $D$ indicates the number of stored data blocks, and $P$ indicates placement-group size.
    The on-chain footprints exclude $O(N)$ staking states common to all DSNs.
}
\label{tab:dsn}
\end{table}

We summarize previous DSNs in \cref{tab:dsn}, comparing them along three dimensions: storage volume, on-chain footprint, and fault tolerance.
Higher storage volume and fault tolerance are preferable, while lower on-chain footprint is desirable.
Next, we explain how their limitations relate to their data placement solutions.

Filecoin~\cite{filecoin}, Sia~\cite{sia} and Shelby~\cite{shelby} achieve scalable storage volume but must trade off between on-chain footprint and fault tolerance.
Their on-chain footprints grow with placement-group size because placement metadata is explicitly recorded as storage contracts.
In practice, they must bound on-chain overhead by using small groups, typically fewer than 10 in Filecoin and 30 by default in Sia.
These group sizes are fixed and do not scale with the network.
As a result, a fraction of Byzantine nodes can dominate individual groups, for example, by offering storage prices that rational nodes cannot sustainably match.
Conversely, tolerating a global Byzantine fraction would require groups that scale with network size, which would make on-chain overhead infeasible.

Permacoin~\cite{permacoin}, Retricoin~\cite{retricoin}, and Arweave~\cite{arweave} achieve constant on-chain footprint, but they trade off storage volume against fault tolerance.
These DSNs do not enforce mandatory placement, that is, no node is required to store specific data, and instead rely on incentives to balance block redundancy.
Because these placement groups are unorganized, they cannot effectively support erasure coding and therefore must rely on replication, with redundancy increasing as group size grows.
If groups do not scale with Byzantine participation, they cannot consistently outnumber Byzantine nodes, which can then cluster within and monopolize specific groups.
If groups do scale with network size, storage volume becomes non-scalable and is constrained by the storage supply of individual nodes.
This is exactly what happens in Arweave, where 350 TiB of data is stored by only around 100 nodes\footnote{\url{https://viewblock.io/arweave}}.

Walrus~\cite{walrus} adopts a data placement approach that more closely resembles traditional storage systems~\cite{ceph}.
In Walrus, the top 1000 nodes (according to their staking) are selected as the committee to store all data for each epoch (of two weeks).
It uses algorithmic placement to map each data block to a subset of committee nodes via a hash function, which yields a scalable on-chain footprint.
However, its storage volume is not scalable, and it is vulnerable to a fraction of Byzantine nodes compromising the committee at sufficient system scale.

Swarm~\cite{swarm} achieves both scalable on-chain footprint and Byzantine tolerance, but falls short in storage volume.
Swarm divides nodes into disjoint neighborhoods.
The nodes in the same neighborhoods replicate the same set of data and share rewards, so nodes are incentivized to shift to less-populated neighborhoods and automatically repair redundancy for their data.
Each data block is routed to a random neighborhood for storage with the help of a distributed hash table (DHT)~\cite{chord,kademlia}, an algorithmic approach that enables constant on-chain overhead.
On the other hand, replication within neighborhoods incurs non-scalable storage volume.
The neighborhood size is limited by practical redundancy level, leading to small neighborhoods vulnerable to Byzantine nodes.
Swarm further employs a cross-neighborhood erasure-coding layer.
Each data block is erasure-coded and redundantly stored in multiple neighborhoods.
Even if a fraction of neighborhoods is compromised by $O(N)$ Byzantine nodes, the remaining encoded fragments can still recover the original data block.
The downside of this approach is that the redundancy loss from failed placement groups can be repaired only manually.
It also requires an additional erasure-coding layer, which introduces extra storage overhead on top of already costly in-neighborhood replication.

% ==== backup materials for full paper ====
\iffalse
\paragraph{Explicit on-chain placement.}
In Filecoin and Sia, users control placement of their data.
They pick storing nodes and sign contracts with them, and the contracts are stored on-chain as explicit placement metadata.
Only the contracted nodes can earn profit by storing the data, and storing the data is mandatory or penalties apply.

Per-node explicit records simplify erasure coding: clients can locally encode data blocks and sign contracts with different nodes to store distinct fragments.
The downside is a large on-chain footprint, because the state for each data block is proportional to the placement group size.
To tolerate the higher failure rates common in DSNs, placement groups must grow, further bloating on-chain state.
Both DSNs attempt to work around this limitation.
Filecoin chooses large storage units (32 GiB or 64 GiB) to reduce the number of tracked data blocks and incentivizes extremely reliable, cluster-grade nodes to secure data with small placement groups, usually under 10 nodes.
Sia targets daily personal use with small storage units and accommodates less reliable nodes with a default placement group size of 30.
This yields overwhelming blockchain state, leading Sia to shift recently to a stateless blockchain paradigm (Utreexo).
As a result, Sia does not permit external clients: all users must remain online to download new block headers, update Merkle proofs of their coins, and monitor and audit the nodes storing their data themselves, since delegation is infeasible in a stateless blockchain.

Moreover, the number of Byzantine nodes these DSNs can tolerate is proportional to the placement group size instead of the total number of nodes.
Byzantine nodes can attack a data block by offering low storage prices and inducing users to sign contracts with them.
Even if users choose contracted nodes purely at random, there remains nontrivial probability that Byzantine nodes dominate initially or during replacement over the data lifetime.
The high on-chain overhead of explicit placement therefore amplifies vulnerability to Byzantine nodes.

\paragraph{Implicit incentive-driven placement.}
Permacoin and Retricoin are research designs for archiving large public static datasets.
They do not enforce data placement but encourage every node to store as much data as possible.
Similar to Bitcoin, nodes are rewarded for successfully mining blocks, which require them to prove storage of specific dataset segments.
The more segments a node stores, the higher its probability of mining a block and earning rewards.
Arweave is a production DSN following a similar approach.
The historical blocks in the blockchain are themselves the stored data, and each mining round requires proving that a random historical block is stored.
This approach allows the stored dataset to be extended dynamically.
All these DSNs achieve constant on-chain footprint.
Only a small accumulator (e.g., Merkle root), representing all persisted data, is required to be stored by the nodes and validate mined blocks.
The size of this accumulator remains constant regardless of the stored data size.

Beyond the difficulty of deleting stored data, these DSNs suffer from poor storage efficiency.
They cannot readily employ erasure coding because miners must prove possession of exact data segments, not coded fragments, to participate in block production.
\sgd{Need further explain why erasure coding is not possible?}
Furthermore, as in the storage contract approach, Byzantine nodes can attack a data segment by collectively storing it and pushing rational nodes to replace it with more profitable segments.
To tolerate Byzantine nodes, the effective placement group size (driven by incentive) must exceed the number of Byzantine nodes.
Consequently, each data segment must be stored on a number of nodes proportional to the total node population to tolerate a global fraction of Byzantine nodes.
This yields high and non-scalable redundancy, feasible only when the system scale is small.
In Arweave, 350 TiB of data is stored by only around 100 nodes.

\paragraph{Disjoint replication.}
Swarm separates nodes into disjoint neighborhoods based on their overlay-network address prefixes.
Data blocks are uniformly routed, via a distributed hash table (DHT), to randomly selected neighborhoods and then replicated by the nodes within those neighborhoods.
This design achieves a constant on-chain footprint.
Storage and retrieval requests can be routed to the responsible neighborhood through the DHT without additional on-chain overhead.
Swarm does not record stored data on chain; instead, it verifies whether nodes within the same neighborhood store identical data.
Leveraging game-theoretic incentives, Swarm can detect faulty nodes as long as each neighborhood contains at least one honest node.

Swarm suffers from limitations similar to those of DSNs with incentive-driven data placement.
It also cannot readily employ erasure coding.
Although data assignment across neighborhoods is randomized, nodes can freely choose which neighborhood to join.
As a result, Byzantine nodes can cluster in specific neighborhoods and displace rational nodes, eventually rendering those neighborhoods insecure.
Swarm must therefore enlarge neighborhood sizes so that each neighborhood can independently tolerate Byzantine concentration, which incurs substantial storage overhead.

\paragraph{Static placement.}
Walrus is an emerging DSN that more closely resembles traditional storage systems.
In Walrus, the top 1000 nodes (according to their staking) are selected as the committee to store all data for each epoch (of two weeks).
A hash function maps each data block to the nodes of its placement group, which collectively store the data with erasure coding.
This design enables both efficient storage and low on-chain footprint, as the on-chain state only needs to store per-data record, and the placement can be solely determined with the hash function.
However, Walrus has limited storage volume because it can draw resources only from 1000 nodes.
Fault tolerance is likewise limited to a fraction of those utilized nodes.
With a large total node population, a fraction of Byzantine nodes may overwhelm the selected committee and cause data loss.
\fi